Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-06-20 paper/tex/sections/conclusion.tex
add simple MW conclusion

Our main conclusions can be summarised as:
\begin{itemize}
    \item \textbf{Detection rate:} We find that on average, for our fiducial model, a 4(10)-year LISA mission will detect \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs and \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
    \item \textbf{Black hole mass distribution:} Due to the high metallicity of the Milky Way, we find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA is skewed heavily towards lower masses, with 88\% and 91\% having masses less than $11 \unit{M_\odot}$ respectively. Moreover, we find that for LISA detectable DCOs, 35\% of BHBHs and 39\% of BHNSs have masses in the theoretical lower mass gap between NSs and BHs.
    \item \textbf{Eccentricity distribution:} Unlike the more numerous WDWD LISA population, we find that BH and NS binaries still have significant eccentricities during the LISA mission. It will therefore be important to consider the analysis of LISA data for eccentric sources as they may have many detectable harmonics. We find that 86(35)\% of BHBHs, 46(16)\% of BHNSs and 86(31)\% of NSNSs have eccentricity of $e > 0.01(0.1)$ at the start of the LISA mission.
    \item \textbf{Physics variations:} For BHBHs, we find that the detection rate is largely unaffected by changes in underlying physics assumptions, except for the optimistic CE scenario and increased Wolf-Rayet winds. Conversely, the BHNS rate varies widely with physics variation, ranging from a mean of 4 to 138. The NSNS shows some variation but only shows large changes under the assumption that case BB mass transfer is unstable and that core-collapse supernovae produce weaker kicks.
    \item \textbf{Distinguishable sources:} For a 4(10)-year LISA mission, we estimate that of the detectable population, at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs will produce signals that are distinguishable from a signal produced by a WDWD. Additionally, we predict that we will be able to determine whether \BHBHDistinguishedFour{}(\BHBHDistinguishedTen{}) BHBHs, \BHNSDistinguishedFour{}(\BHNSDistinguishedTen{}) BHNSs and \NSNSDistinguishedFour{}(\NSNSDistinguishedTen{}) NSNSs are signals from a binary that contains a black hole.
    \item \textbf{Joint SKA-LISA detections:} Using some analytical estimations, we approximately predict that \textit{if} the binary contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of pulsars that could crowd the sky in SKA-2 means that this total decreases to 6. This total could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.
    \item \textbf{Importance of metallicity-dependent MW model:} \tom{I'll fill this in with whatever I find in my sim (see subsection in discussion)}
\end{itemize}

>>>>

Our main conclusions can be summarised as:
\begin{itemize}
    \item \textbf{Detection rate:} We find that on average, for our fiducial model, a 4(10)-year LISA mission will detect \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs and \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
    \item \textbf{Black hole mass distribution:} Due to the high metallicity of the Milky Way, we find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA is skewed heavily towards lower masses, with 88\% and 91\% having masses less than $11 \unit{M_\odot}$ respectively. Moreover, we find that for LISA detectable DCOs, 35\% of BHBHs and 39\% of BHNSs have masses in the theoretical lower mass gap between NSs and BHs.
    \item \textbf{Eccentricity distribution:} Unlike the more numerous WDWD LISA population, we find that BH and NS binaries still have significant eccentricities during the LISA mission. It will therefore be important to consider the analysis of LISA data for eccentric sources as they may have many detectable harmonics. We find that 86(35)\% of BHBHs, 46(16)\% of BHNSs and 86(31)\% of NSNSs have eccentricity of $e > 0.01(0.1)$ at the start of the LISA mission.
    \item \textbf{Physics variations:} For BHBHs, we find that the detection rate is largely unaffected by changes in underlying physics assumptions, except for the optimistic CE scenario and increased Wolf-Rayet winds. Conversely, the BHNS rate varies widely with physics variation, ranging from a mean of 4 to 138. The NSNS shows some variation but only shows large changes under the assumption that case BB mass transfer is unstable and that core-collapse supernovae produce weaker kicks.
    \item \textbf{Distinguishable sources:} For a 4(10)-year LISA mission, we estimate that of the detectable population, at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs will produce signals that are distinguishable from a signal produced by a WDWD. Additionally, we predict that we will be able to determine whether \BHBHDistinguishedFour{}(\BHBHDistinguishedTen{}) BHBHs, \BHNSDistinguishedFour{}(\BHNSDistinguishedTen{}) BHNSs and \NSNSDistinguishedFour{}(\NSNSDistinguishedTen{}) NSNSs are signals from a binary that contains a black hole.
    \item \textbf{Joint SKA-LISA detections:} Using some analytical estimations, we approximately predict that \textit{if} the binary contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of pulsars that could crowd the sky in SKA-2 means that this total decreases to 6. This total could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.
    \item \textbf{Importance of metallicity-dependent MW model:} The use of Milky Way models that use fixed metallicity populations which are assigned irrespective of birth time or position may lead to an overestimation of the LISA NSNS detection rate. It may also introduce unphysical artifacts into DCO parameter distributions, particularly the mass distributions, which lead to inaccurate predictions.
\end{itemize}
